---
title: "Week 3 - Start with R"
author: "Emil Bæk Mogensen"
date: "2023-09-18"
output:
  pdf_document: default
  html_document: default
---

---
title: "Week 3 - Start with R"
author: "Emil Bæk Mogensen"
date: "2023-09-14"
output:
  pdf_document: default
  html_document: default
---
Packages
```{r}
library(tidyverse)
```

For this assignment, please answer the following three questions showing your code and results and then take a particular screenshot of your working environment. You can upload here (to Brightspace) the code and the URL to the screenshot OR submit everything to Github and submit here a single link to your repository.


1) Use R to figure out how many elements in the vector below are greater than 2.

```{r}
rooms <- c(1, 2, 1, 3, 1, NA, 3, 1, 3, 2, 1, NA, 1, 8, 3, 1, 4, NA, 1, 3, 1, 2, 1, 7, 1, NA)
rooms <- rooms[!is.na(rooms)]
length(rooms[rooms > 2])
```
2) What type of data is in the 'rooms' vector? 
```{r}
class(rooms)
```


3) What is the result of running the median() function on the above 'rooms' vector?

```{r}
median(rooms)
```
# 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)